%
%

\begin{abstract}
% A space is needed before the text starts so that the first paragraph
% is indented properly. Max 350 words.

    % TODO: Rewrite
    In early 2020, the United States Congress passed a resolution to permit the
    use of proxy voting during emergencies for members of the House of Representatives.
    Proxy voting is a system of voting where a voter can assign another voter, called
    a proxy or a delegate, to vote on their behalf.
    As with other voting systems, the votes are then aggregated into a final result
    using a voting rule or mechanism.
    Ideally, the result of proxy voting would be the same, or as close to as
    possible, to the result if everyone were to vote.
    The type of proxy voting used in Congress differs from the traditional
    definition of proxy voting in that proxies are required to vote as directed, and
    was designed to reduce the transmission of disease such as COVID-19.
    If traditional proxy voting can be shown to be beneficial, the resolution could be
    adapted and expanded to create a more efficient government system.
    However, proxy voting in Congress has been regarded with some skepticism and the
    question remains as to if proxy voting has too great of an effect on the result
    of the vote.
    As such, there is a need to determine to what degree proxy voting produces
    error when compared to traditional direct voting, if at all, in order to ensure it
    cannot be abused and lead to undesirable or unfair results.
    In this study, we explore the effects of proxy voting on the results of a vote
    under a number of preference distributions.
    We additionally explore how different voting rules affect the results of the vote.
    We employ an opinion space model and determine the result of a vote as a point in
    the model space, instead of the vote simply passing or failing, in order to
    increase the granularity of the results and determine how much error is
    introduced due to proxy voting.
    Finally, we attempt to determine how many proxies a voter should be allowed
    to delegate for an individual vote in order to increase the accuracy of the system
    as compared to proxy voting with a single proxy.
    \vicki{Need to make it clear we are talking about a single vote being divided
    between multiple proxies.}
    % TODO: Put in a bit of what we discover


\end{abstract}


% Local Variables:
% TeX-master: "newhead"
% End:
